\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{hyperref}

\titleformat{\section}{\Large\bfseries}{\thesection.}{0.5em}{}
\setstretch{1.2}

\begin{document}

\begin{titlepage}
    \centering
    {\Huge \textbf{Data Dictionary}}\\[1.5em]
    {\Large Generated with the assistance of ChatGPT}\\[1em]
    {\large \today}
\end{titlepage}

\tableofcontents
\newpage

% =========================
\section{USER Table}
% =========================

\begin{longtable}{@{}p{4cm}p{3cm}p{6cm}p{3cm}@{}}
\toprule
\textbf{Field Name} & \textbf{Data Type} & \textbf{Description} & \textbf{Constraints} \\ \midrule
\endhead
name & Complex & The name of the user. & --- \\
f\_name & varchar(250) & User’s first name. & --- \\
m\_name & varchar(250) & User’s middle name. & --- \\
l\_name & varchar(250) & User’s last name. & --- \\
institution & varchar(250) & The name of the institution that the user is a part of. & UNIQUE \\
user\_id & char(20) & An ID generated for the user. & PRIMARY KEY \\
email & varchar(250) & The user’s email address. & UNIQUE, NOT NULL \\
hashed\_password & varchar(250) & The password hash used for authentication. & NOT NULL \\
Research\_fields & varchar(250) & The fields of research the user is interested in obtaining grants for. & --- \\ 
\bottomrule
\end{longtable}

% =========================
\section{DOCUMENTS Table}
% =========================

\begin{longtable}{@{}p{4cm}p{3cm}p{6cm}p{3cm}@{}}
\toprule
\textbf{Field Name} & \textbf{Data Type} & \textbf{Description} & \textbf{Constraints} \\ \midrule
\endhead
document\_name & varchar(250) & The name of the document. & --- \\
upload\_date & date & The date the document was uploaded. & --- \\
document\_id & char(20) & A unique identifier for the document. & PRIMARY KEY \\
document\_type & varchar(10) & The type of file. & --- \\
document\_size & int & The size of the document. & --- \\
application\_id & char(20) & Identifier linking the document to an application. & FOREIGN KEY \\ 
\bottomrule
\end{longtable}

% =========================
\section{APPLICATION Table}
% =========================

\begin{longtable}{@{}p{4cm}p{3cm}p{6cm}p{3cm}@{}}
\toprule
\textbf{Field Name} & \textbf{Data Type} & \textbf{Description} & \textbf{Constraints} \\ \midrule
\endhead
application\_id & char(20) & Unique identifier for the application. & PRIMARY KEY \\
status & varchar(250) & The current status of the application. & --- \\
grant\_id & char(20) & Identifier for the related grant. & FOREIGN KEY \\
user\_id & char(20) & Identifier for the user who submitted the application. & FOREIGN KEY \\
\bottomrule
\end{longtable}

% =========================
\section{INTERNAL DEADLINES Table}
% =========================

\begin{longtable}{@{}p{4cm}p{3cm}p{6cm}p{3cm}@{}}
\toprule
\textbf{Field Name} & \textbf{Data Type} & \textbf{Description} & \textbf{Constraints} \\ \midrule
\endhead
deadline\_id & char(20) & A unique identifier for the internal deadline. & PRIMARY KEY \\
deadline\_name & varchar(250) & The name of the deadline. & --- \\
deadline\_date & date & The date that the deadline applies to. & --- \\
application\_id & char(20) & Identifier for the related application. & FOREIGN KEY \\
\bottomrule
\end{longtable}

% =========================
\section{GRANT Table}
% =========================

\begin{longtable}{@{}p{4cm}p{3cm}p{6cm}p{3cm}@{}}
\toprule
\textbf{Field Name} & \textbf{Data Type} & \textbf{Description} & \textbf{Constraints} \\ \midrule
\endhead
grant\_id & char(20) & Unique identifier for the grant. & PRIMARY KEY \\
Grant\_title & varchar(255) & The title of the grant. & --- \\
description & varchar(18000) & Detailed description of the grant. & --- \\
Research\_field & varchar(250) & The research field of the grant. & --- \\
Expected\_award\_count & int & The number of awards expected to be issued. & --- \\
eligibility & varchar(4000) & Eligibility criteria for the grant. & --- \\
award\_max\_amnt & int & Maximum amount that can be awarded. & --- \\
award\_min\_amnt & int & Minimum amount that can be awarded. & --- \\
program\_funding & int & Total funding available for the grant. & --- \\
provider & varchar(255) & The organization providing the grant. & --- \\
link\_to\_source & varchar(250) & Link to the official grant listing. & --- \\
point\_of\_contact & varchar(3000) & Point of contact for the grant. & --- \\
date\_posted & date & The date the grant was posted. & --- \\
Archive\_date & date & The date the grant was archived. & --- \\
date\_closed & date & The date the grant was closed. & --- \\
last\_update\_date & date & The date the grant information was last updated. & --- \\
\bottomrule
\end{longtable}

\vfill
\begin{center}
    {\footnotesize \textit{This data dictionary was generated with the assistance of ChatGPT.}}
\end{center}

\end{document}